Experiment 1a (Root Questions in Context): Pre-processing

### 2022-11-13 analysis/03_experiment/rscripts/pre-processing.Rmd
main.text

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../helpers.R")
```

@@

length(unique(failed_controls$workerid)) # 35
length(unique(failed_controls$workerid))/length(unique(d$workerid))*100 # 5.5%
```

@@

ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=ModalPresent)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  facet_wrap(~Wh) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/test_ModxWh.pdf")

@@

data_summary <- function(x) {
   m <- mean(x)
   ymin <- m-sd(x)
   ymax <- m+sd(x)
   return(c(y=m,ymin=ymin,ymax=ymax))
}

@@

```{r}
ggplot(agr, aes(x=paraphrase, y=mean_rating,fill=paraphrase, color=paraphrase)) + 
  geom_violin(trim=FALSE,alpha=.4) +  
  geom_dotplot(binaxis='y', stackdir='center',stackratio=1, dotsize=1.2) +
    stat_summary(fun=data_summary, geom="point", shape=18,
                 size=3, color="red") +
    # geom_jitter(shape=16, position=position_jitter(0.2)) +
    # geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  ylim(0,1) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/1a_violin.pdf",width=4,height=2)
```

>>>>

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(tidyverse)
# library(Hmisc)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../helpers.R")
```

@@

length(unique(failed_controls$workerid)) # 35
length(unique(failed_controls$workerid))/length(unique(d$workerid))*100 # 3.5%
```

@@

ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=ModalPresent)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  facet_wrap(~Wh) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/test_ModxWh-raw.pdf")

@@

@@

```{r}

data_summary <- function(x) {
   m <- mean(x)
   ymin <- m-ci.low(m)
   ymax <- m+ci.high(m)
   return(c(y=m,ymin=ymin,ymax=ymax))
}

data_summary(agr)

sum <- agr %>% 
  group_by(paraphrase) %>% 
  summarize(GrandMean = mean(mean_rating), CILow = ci.low(mean_rating), CIHigh = ci.high(mean_rating)) %>%
  mutate(YMin = GrandMean - CILow, YMax = GrandMean + CIHigh) %>%
  drop_na()

View(sum)

ggplot(agr, aes(x=paraphrase, y=mean_rating,fill=paraphrase, color=paraphrase)) + 
  geom_violin(trim=FALSE,alpha=.4) +  
  # geom_dotplot(binaxis='y', stackdir='center',stackratio=1, dotsize=1) +
  # stat_summary(fun.data = sum, geom="point", size=3) +
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
                width = 0.2) +
    # geom_jitter(shape=16, position=position_jitter(0.2)) +
  # geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  ylim(0,1) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/1a_violin.pdf",width=4,height=2)
```
